P-Threads strikes back

### 2017-07-21 sections/04-researchdesign.tex
Adding initial research questions

>>>>

\begin{description}
\item[RQ1:] \textit{Which API is easier to learn and use for beginning students?}
%
...
\item[RQ2:] \textit{Which API is better to improve the performance for beginning students?}
%
...
\item[RQ3:] \textit{Which API is easier to learn and use for advanced students?}
%
...
\item[RQ4:] \textit{Which API is better to improve the performance for advanced students?}
%
...

\end{description}
